A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-10 paper/paper.Rnw
need to fix explanation of conf matrix

In the confusion matrix presented in \autoref{fig:confusion_matrix}, the values along the diagonal represent the proportion of true positives captured within each category. The off-diagonal values represent the proportion of false positives for each shape pairing; however, since a single image may truly contain multiple shapes, the values have been adjusted to remove the effect of any true positives from the calculation of false positive proportions. \svp{I can't remember exactly how we're doing that, but we may want to look more closely at that - if we set everything to NA instead of 0, the rate calculations would be higher than expected} \mt{They're being set to NA, and then we're calculating proportions with na.rm = T. I don't understand what you mean about higher rates than expected...}. For example, to calculate the proportion of images that contain triangles but are being falsely labeled as containing quadrilaterals, any image that truly contains both triangles and quadrilaterals is removed before calculating the proportion of false quadrilateral labels.

>>>>

In the confusion matrix presented in \autoref{fig:confusion_matrix}, the values along the diagonal represent the proportion of true positives captured within each category. The off-diagonal values represent the proportion of false positives for each shape pairing; however, since a single image may truly contain multiple shapes, the values have been adjusted to remove the effect of any true positives from the calculation of false positive proportions. \svp{As a result of this adjustment, the probabilities off-diagonal are the proportion ... need to explain the conditional probability we're showing here} %\svp{I can't remember exactly how we're doing that, but we may want to look more closely at that - if we set everything to NA instead of 0, the rate calculations would be higher than expected} \mt{They're being set to NA, and then we're calculating proportions with na.rm = T. I don't understand what you mean about higher rates than expected...}.
For example, to calculate the proportion of images that contain triangles but are being falsely labeled as containing quadrilaterals, any image that truly contains both triangles and quadrilaterals is removed before calculating the proportion of false quadrilateral labels.
